---
title: "p8105_hw6_jy3270"
author: "Jingya Yu"
date: "2022-12-01"
output: github_document
---
```{r, include = FALSE}
library(tidyverse)
```

## Problem 2
- import the data
```{r}
homicide <- read_csv("./data/homicide-data.csv") %>% janitor::clean_names()
head(homicide)
```

- Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.

```{r}
homicide <- homicide %>%
  mutate(city_state = str_c(city, ", ", state),
        status = case_when(disposition == "Open/No arrest" ~ 0,
                   disposition == "Closed by arrest" ~ 1,
                   disposition == "Closed without arrest" ~ 0
        ),
        victim_age = as.numeric(victim_age)) %>%
        drop_na() %>%
        filter(victim_race %in% c("White", "Black"),
               city_state != "Dallas, TX",
               city_state != "Phoenix, AZ",
               city_state != "Kansas City, MO",
               city_state != "Tulsa, AL")
head(homicide)
```
- For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; 

```{r}
Baltimore = homicide %>% filter(city_state == "Baltimore, MD")
Baltimore_fit = glm(status ~ victim_age + victim_race + victim_sex, data = Baltimore, family = binomial())

```

- Apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.
```{r}
Baltimore_fit %>%
  broom::tidy(conf.int = T, conf.level=0.95) %>% 
  mutate(OR = exp(estimate),
         conf_low = exp(conf.low),
         conf_high = exp(conf.high)) %>%
  select(term, OR, conf_low, conf_high) %>% 
  knitr::kable(digits = 3)
```

- Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims.

```{r}
glm_function = function(name) {
  fit = homicide %>%
    filter(city_state == name) %>%
    glm(status ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) %>%
    broom::tidy(conf.int = T, conf.level=0.95) %>% 
    mutate(OR = exp(estimate),
           conf_low = exp(conf.low),
           conf_high = exp(conf.high)) %>%
    select(term, OR, conf_low, conf_high)
  return(fit)
}
```

-Create a dataframe with estimated ORs and CIs for each city.

```{r}
all_result = tibble(
   city_states = unique(homicide$city_state),
  all_fits = map(city_states, glm_function)
  ) %>% unnest(all_fits) %>%
  filter(term == "victim_sexMale")

all_result
```

- Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}
all_result %>% 
  mutate(city_states = fct_reorder(city_states, OR)) %>%
  ggplot(aes(x = OR, y = city_states)) +
  geom_point() +
  geom_errorbar(aes(xmin = conf_low, xmax = conf_high)) +
  ggtitle("estimated ORs and CIs for each city") +
  xlab("Odds ratio") +
  ylab("City")
```

According the background of out analysis, a high estimated OR indicates that homicide cases of male are more likely to be solved than female's case. Albuquerque, NM has the highest OR, which means that homicide cases of male are most likely to be solved compared to other cities, if we keep victims' age and race fixed. On the other hand, New York NY has the lowest estimated OR, which means that homicide cases of female are most likely to be solved than other cities, if we keep victims' age and race fixed.

